\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage{scrextend}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{relsize}  % For \textscale
\usepackage[protrusion]{microtype}  % needs an obscure package
\usepackage{enumitem}
\usepackage{indentfirst}
\usepackage{ragged2e}
\usepackage{xspace}
\usepackage{lmodern}

\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\hypersetup{colorlinks,
            linkcolor={dark-blue},
            citecolor={dark-blue},
            urlcolor={DarkGreen}}


%\setmainfont[
%    Ligatures ={Common, TeX},
%    Path      =/usr/share/fonts/ttf-linux-libertine/,
%    Extension =.ttf
%]{LinLibertine}
\hyphenation{Some-long-word}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\xspaceskip7pt  % some more spacing between sentences
% use "i.e.\ " or "with SQL\@. " in case of errors

\newcommand{\HRule}[1][\medskipamount]{\par
  \vspace*{\dimexpr-\parskip-\baselineskip+#1}
  \noindent\rule{\linewidth}{0.4pt}\par
  \vspace*{\dimexpr-\parskip-.5\baselineskip+#1}}

\NewDocumentEnvironment{mysection}{m O{}}{%
    \noindent
    {\hspace{0.5em}\normalfont\LARGE #1} \hfill #2%
    \HRule{}
    \medskip
}{\bigskip}

\newenvironment{worksection}[3]{
    \begin{addmargin}[0.5em]{0em}
    {\large\bfseries #1} \hfill {\bfseries #2}\\%
    \hspace*{1em}#3
    \begin{itemize}
        [label=-, topsep=0pt, itemsep=0.5ex, parsep=0pt, leftmargin=1em]
}{
    \end{itemize}
    \end{addmargin}
    \medskip
}

\newenvironment{headedsection}[2]{
    \begin{addmargin}[0.5em]{0em}
    {\large\bfseries #1} \hfill {\bfseries #2}%
    \begin{itemize}
        [label=-, topsep=0pt, itemsep=0.5ex, parsep=0pt, leftmargin=1em]
}{
    \end{itemize}
    \end{addmargin}
    \medskip
}

\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\sim$}}

\newcommand{\archive}{https://web.archive.org/web}

\newcommand{\FadleyGroup}{
  \href{\archive/20201001085257/http://fadley.physics.ucdavis.edu/}
       {Fadley Group}
}

\newcommand{\Noisebridge}{
  \href{https://www.noisebridge.net/}{Noisebridge}.
}

\newcommand{\ComputationalPhysics}{
  \href{http://young.physics.ucsc.edu/115/}{Computational Physics}
}

\newcommand{\MathematicalMethods}{
  \href{http://scipp.ucsc.edu/~haber/ph116C/}{Mathematical Methods}
}

\begin{document}
\sloppy  % relax whitespace in favor of straight margins

\noindent{\LARGE\textbf{Jared Garst}}

\vspace{1em}

\begin{mysection}{Experience}[
    Python
    \textbullet{} SQL
    \textbullet{} Linux
    \textbullet{} Operations
    \textbullet{} Analysis
    \textbullet{} Resilience
]

  \begin{worksection}
        {Senior Software Engineer, Data}
        {2022--current, LaunchDarkly}
        {Python -- SQL -- AWS -- Terraform -- dbt -- Snowflake -- Fivetran -- Airflow -- Looker}
%       {Expanding a feature flagging product by refining pricing, marketing,
%        and product lines.}


    \item Built most of the infrastructure for ingestion into our main analytics
          warehouse.
    \\    Managed organic adoption by multiple other teams.

    \item Established and refined development operations - deployment, CI,
          tagging compliance.
    \\    Focused on team speed and effectiveness.
          Widely praised for being a joy to work with.

    \item Found and was sometimes point person for resolving a number of
          emergencies.
    \\    Incorrect billing numbers, emails not being sent,
          an abandoned 15TB/month pipeline.

  \end{worksection}

  \begin{worksection}
        {Senior Software Engineer, Data}
        {2021--2022, Afresh}
        {Python -- SQL -- Spark -- Snowflake}
%       {Minimized food waste at grocery stores by predicting how much produce
%        should be ordered.}

    \item Created resilient pipelines, in anticipation of timing and hygiene
          issues within the nightly data dump.
    \item Integrated new customers, bridging quirks in their data with the
          assumptions of our model.
    \item Mentored junior developers.  Provided low stakes direction of effort
          and sharpening of understanding.
    \item Framed and scoped work, provided context and steered team towards
          high impact areas.

  \end{worksection}

  \begin{worksection}
        {Software Engineer, Data}
        {2019--2021, Grand Rounds}
        {SQL -- Redshift -- Looker}
%       {Managed and maintained data resources for complex health care
%        organization.}

    \item Combined heterogeneous sources to deliver hygienic data on time,
          with usable interfaces and SLAs.
%   \item Developed the data model to answer qualitative questions from 4
%         distinct teams.
%   \item Migrated critical but unmaintained 51 step data pipeline to a new
%         query engine and ETL system.
    \item Created systems that process sensitive personal health information
          through masking and aggregation.
%   \item Started and fostered a practice of documentation and testing for
%         unloved processes.

  \end{worksection}


    \begin{addmargin}[0.5em]{0em}
    {\large\bfseries Software Engineer and Mentor}
    \hfill {\bfseries 2019, Pathrise}\\%
    \hspace*{0ex}Career Services and tutoring for new grad software engineers.

%   \begin{itemize}
%       [label=-, topsep=0pt, itemsep=0.5ex, parsep=0pt, leftmargin=1em]
%
%   \item Python and statistics expert in a software engineering mentorship 
%         and placement program.
%
%   \end{itemize}

    \end{addmargin}
    \medskip

  \begin{worksection}
        {Software Engineer}
        {2017--2018, Emerald Cloud Labs}
        {Software tools and data interfaces for an automated biology lab.}

    \item Implemented an ORM that powered biology experiments and data retrieval.
%   \item Created hundreds of unit tests, many integration tests and some
%         property based tests.
    \item Wrote documentation and designs for scientists with minimal coding
          experience.
%   \item Solved project management problems, saw efforts through to completion.

  \end{worksection}

  \begin{worksection}
        {Graduate Researcher, \FadleyGroup}
        {2013--2016, University of California, Davis}
        {Experimental observation of material electronic structure.}

%   \item Reconstructed electronic structure of materials by observing
%         electrons ejected with x-rays.
    \item Collected and performed statistical analysis on gigabyte-sized lists
          of electron strikes.
%   \item Refactored and deployed simulation codes in Python, C, Matlab, and
%          Fortran.
%   \item Acted as group sysadmin, provisioning servers and teaching coding
%         skills.

  \end{worksection}

\end{mysection}

\begin{mysection}{Projects}[
    Education \textbullet{} Technical Communication \textbullet{} Community
]

\begin{headedsection}
     {Python Educator}
     {2018--current}

    \item Years of teaching to many learning profiles and in many contexts.
    \item Currently runs a weekly working group with friends and family.
    \\    Two members have transitioned into software engineering roles.
    \item Organized and taught a weekly introductory Python class at
          \Noisebridge{}.
%   \item Has taught a broad range of backgrounds, including biologists,
%         junior developers and the retired.

  \end{headedsection}

%   \begin{worksection}{TripleByte Certified}
%       \item Two hour intensive technical interview
%   \end{worksection}

\end{mysection}

\begin{mysection}{Education}
\begin{headedsection}
      {PhD, did not finish --- Physics}
      {University of California, Davis}
    \item Advanced coursework in statistical, quantum and condensed matter
          physics.
%   \item Passed multi-day end of year exam with an excellent score.

  \end{headedsection}

  \begin{headedsection}{Bachelor of Science --- Physics}
        {University of California, Santa Cruz}
    \item Completed degree in $2.5$ years with $3.86$ in major GPA.
    \item Received top grade in many classes, including \ComputationalPhysics{}
          and \MathematicalMethods{}.

  \end{headedsection}
\end{mysection}

\vfill

\begin{center}
    If you have any questions, please contact me at
\end{center}

\begin{center}
  \href{https://github.com/jgarst}{https://github.com/jgarst}
  \textbullet{}
  \href{mailto:jhg@fastmail.com}{jhg@fastmail.com}
  \textbullet{}
  \href{https://www.linkedin.com/in/jgarst}
       {https://www.linkedin.com/in/jgarst}
\end{center}

\end{document}
