%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\setmainfont[Ligatures={Common, TeX}]{Linux Libertine O}
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
% blue links

\usepackage{xpatch}
\xpatchcmd{\makeletterclosing}{[3em]}{[0em]}{}{}

% justified text
\usepackage{etoolbox}
\makeatletter
\patchcmd{\makeletterhead}
    {\raggedright \@opening}
    {\@opening}
    {}{}
\makeatother
% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates

% personal data
\name{Jared}{Garst}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{~}{~}
\date{\today}
\opening{Dear Alloy,}
\closing{All the best,}
\makelettertitle%

I was pleased to find your posting for the Data Engineer position on the Hacker News job thread.
My experience managing research data and statistics, I think my skills are an excellent fit for the work.
Please find my resume included, I'm excited to apply.

I have worked independently to empower scientists with software for the past 3 years.
When I was teaching I saw that the `tell students to google it' strategy wasn't working, and filled that gap by writing them programming guides.
In my research group, I made simple, usable technology decisions that kept our software working and the data flowing.
My current job allows biologists to view their data across time, sample, or any other dimension they find productive.

I am proud of this work, but think my communication successes are an even better recommendation for the position.
My most productive time is spent talking with customers.
I have saved countless hours by finding out what our users want and why they want it.
I also spend lots of time helping people in mundane ways.
I have taught basic git enough times that I can get people productive within one sitting, covering the concepts in concrete terms and keeping them engaged through the process.

I look forward to bringing these abilities to my next job --- I sincerely hope it will be Citrine.

\makeletterclosing%

\end{document}


%% end of file `template.tex'.
