%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\setmainfont[Ligatures={Common, TeX}]{Linux Libertine O}
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
% blue links

\usepackage{xpatch}
\xpatchcmd{\makeletterclosing}{[3em]}{[0em]}{}{}

% justified text
\usepackage{etoolbox}
\makeatletter
\patchcmd{\makeletterhead}
    {\raggedright \@opening}
    {\@opening}
    {}{}
\makeatother
% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates

% personal data
\name{Jared}{Garst}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{~}{~}
\date{\today}
\opening{Dear Honeycomb,}
\closing{All the best,}
\makelettertitle%

I came across the Solutions Engineer position and was struck by how close the position is to my previous work.
Your company advocates for standardized, sampled event data and beautiful, reproducible analyses.
I have spent many years working with high cardinality scientific data, and think that these ideas are life changing, but that too many people haven't heard the good news.
Please find my resume included, I'm excited to apply.

I have worked independently to empower people with software for the past 3 years.
When I was teaching, I saw that the `tell students to google it' strategy wasn't working, and filled that gap by writing them \textcolor{cyan}{\href{https://github.com/jgarst/AdvancedLab/releases/download/spring_2016/Python-FirstSteps.pdf}{programming guides}}.
In my research group, I made simple, usable technology decisions that kept our software working.
In my current work, I measure success by how much complexity I can keep off my manager's plate.

I am proud of this work, but think my communication successes are an even better recommendation for the position.
My most productive time is spent talking with customers.
I have saved countless hours by finding out what our users want and why they want it.
I also spend lots of time helping people in mundane ways. I have taught basic git enough times that I can get people productive within one sitting, covering the concepts in concrete terms and keeping them engaged through the process.
I volunteer for documentation tasks that no one else wants to do.
I attend community project nights, and spend most of that time with the people who have been coding for two weeks.
And not only am I comfortable with these skills, I am genuinely enthusiastic about them.
My favorite programming concepts are the ones that democratize and communicate, like the \textcolor{cyan}{\href{https://blog.codinghorror.com/falling-into-the-pit-of-success/}{'pit of success'}}, Hadley Wickham's \textcolor{cyan}{\href{https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html}{tidy data}}, the \textcolor{cyan}{\href{https://www.recurse.com/code-of-conduct}{RC code of conduct}}, or python \textcolor{cyan}{\href{http://arnavk.com/posts/python-context-managers/}{context managers}}.

I look forward to bringing this enthusiasm to my next job --- I sincerely hope it will be at Honeycomb.

\makeletterclosing%

\end{document}


%% end of file `template.tex'.
