%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\setmainfont[Ligatures={Common, TeX}]{Linux Libertine O}
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

\usepackage{xpatch}
\xpatchcmd{\makeletterclosing}{[3em]}{[0em]}{}{}

% justified text
\usepackage{etoolbox}
\makeatletter
\patchcmd{\makeletterhead}
    {\raggedright \@opening}
    {\@opening}
    {}{}
\makeatother
% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates

% personal data
\name{Jared}{Garst}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{~}{~}
\date{\today}
\opening{Dear Splice,}
\closing{All the best,}
\makelettertitle

I came across the Senior Backend Engineer position through the twitter of Ernie Miller, who seems determined to build a team that gets things done through empathy.
Please find my resume included, I'm excited to apply.

I am proud of my technical skills and achievements, but I think my communication successes are an even better recommendation for the position.
My most productive time is spent talking with customers.
I have saved countless hours by finding out what our users want and why they want it.
I have also spent enough time teaching basic git that I can get people productive within one sitting, covering the concepts in concrete terms and keeping them engaged through the process.
Not only am I comfortable with these skills, I am genuinely enthusiastic about them.
I volunteer for documentation tasks that no one else wants to do.
I attend community project nights, and spend most of that time with the people who have been coding for two weeks.
My favorite programming concepts are the ones that democratize and communicate, like the \textcolor{cyan}{\href{https://blog.codinghorror.com/falling-into-the-pit-of-success/}{'pit of success'}}, Hadley Wickham's \textcolor{cyan}{\href{https://cran.r-project.org/web/packages/tidyverse/vignettes/manifesto.html}{tidy data}}, the \textcolor{cyan}{\href{https://www.recurse.com/code-of-conduct}{RC code of conduct}}, or python \textcolor{cyan}{\href{http://arnavk.com/posts/python-context-managers/}{context managers}}.

I look forward to bringing this enthusiasm to my next job -- I sincerely hope it will be at Splice.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
